### 2020-06-02 old/documents/Notes/inequality_demo_temp.tex
figuring out a problem with WagonWheel inequality

\begin{document}
    The current WagonWheel inequality we are using in the paper is the following:
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheel} : \\
        + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
        - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
        - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
        - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
        - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
        - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
        - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
        - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
        - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
        - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
        - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}

>>>>

\begin{document}

    \section{June 1, 2020:}
    As of today, it appears that there is an error in the WagonWheel inequality that ended up in the final manuscript (i.e. $I\tsb{WagonWheelAlternativeProperSwap}$). Specifically, the uniform distribution over all six bits $A_l, A_r, B_l, B_r, C_l, C_r$, which is causally compatible with the Triangle network, actually violates $I\tsb{WagonWheelAlternativeProperSwap}$:  
    \[ I\tsb{WagonWheelAlternativeProperSwap}\left(\frac{1}{2^6}\right) = +\left(\frac{1}{2}\right)^2-\left(\frac{1}{2}\right)^4+\left(\frac{1}{2}\right)^4+\left(\frac{1}{2}\right)^4\cdots\]
    \[\cdots-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8 = \frac{19}{64} \not \leq 0.\]
    Therefore, $I\tsb{WagonWheelAlternativeProperSwap}$ is clearly an invalid inequality and a mistake was introduced somewhere. The actually inequality that Elie proposed was $I\tsb{WagonWheelAlternative}$. In order to make the inequality in the paper correspond to the Fritz distribution in the paper, wherein $C_lC_r = 11$ plays the distinguished role, I attempted to flip the bits for $C_r$ and $B_l$ and erroneously derived $I\tsb{WagonWheelAlternativeProperSwap}$. The \textit{correct} version would have been:
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheelCorrectBitFlip} : \\
        -P_{A_{l}B_{l}}(11) \\
        +P_{A_{l}B_{l}C_{l}C_{r}}(1111) \\
        -P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) \\
        -P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        +P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) \\
        +P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) \\
        -P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        \leq 0
    \end{gathered}
    \end{equation*}
    This inequality when evaluated at the Fritz distribution ($P_F$) reads term by term:
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheelCorrectFlip}(P_F) : \\
        -\frac{1}{4}
        +\frac{1}{4}
        -\left(\frac{1}{4}\right)^2
        -\left(\frac{1}{4}\right)^2\\
        +\frac{1}{4}\left(\frac{1}{32}\left(2-\sqrt{2}\right)\right)
        +\frac{1}{4}\left(\frac{1}{32}\left(2-\sqrt{2}\right)\right)
        -\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
        -\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right) \\
        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right)
        +\frac{1}{4}\left(\frac{1}{32}\left(2+\sqrt{2}\right)\right) \\
        =-\frac{1}{16} \leq 0
    \end{gathered}
    \end{equation*}
    Additionally, this inequality when evaluated at the uniform distribution reads term by term:
    \[ I\tsb{WagonWheelCorrectFlip}\left(\frac{1}{2^6}\right) = -\left(\frac{1}{2}\right)^2+\left(\frac{1}{2}\right)^4-\left(\frac{1}{2}\right)^4-\left(\frac{1}{2}\right)^4\cdots\]
    \[\cdots+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8-\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8+\left(\frac{1}{2}\right)^8 = -\frac{19}{64} \leq 0\]
    Upon closer inspection, $I\tsb{WagonWheelCorrectFlip}$ is identical to the inequality found in the paper, with the direction of inequality reverse (i.e. it was off by an overall minus sign).

    Therefore, it appears that either 1) I have isolated the wrong variables to bit-flip in Elie's $I\tsb{WagonWheelAlternative}$, 2) $I\tsb{WagonWheelAlternative}$ was transcribed from Elie incorrectly, 3) $I\tsb{WagonWheelAlternative}$ is incapable of witnessing the Fritz distribution, or 4) $I\tsb{WagonWheelAlternative}$ is not a valid inequality in the first place.

    I suspect the resolution is of type 2) because the Fritz distribution is all about the agreement or disagreement between $A_r$ and $B_r$ in four different $C_lC_r$ contexts, and $I\tsb{WagonWheelAlternative}$ seems to have $A_r = B_r$ in two contexts and $A_r \neq B_r$ in the other two contexts, which is unlike the form of the Fritz distribution.

    \section{September 18, 2017:}
    The current WagonWheel inequality we are using in the paper is the following:
    \begin{equation*}
    \begin{gathered}
        \eq
        I\tsb{WagonWheel} : \\
        + P_{ABC}(000)P_{C}(3) - 2P_{ABC}(203)P_{C}(0) - 2P_{ABC}(303)P_{C}(0) - P_{ABC}(003)P_{C}(0) \\
        - P_{ABC}(013)P_{C}(0) - P_{ABC}(020)P_{C}(2) - P_{ABC}(022)P_{C}(2) - P_{ABC}(023)P_{C}(0) \\
        - P_{ABC}(023)P_{C}(2) - P_{ABC}(030)P_{C}(2) - P_{ABC}(031)P_{C}(2) - P_{ABC}(032)P_{C}(2) \\
        - P_{ABC}(033)P_{C}(0) - P_{ABC}(033)P_{C}(2) - P_{ABC}(103)P_{C}(0) - P_{ABC}(113)P_{C}(0) \\
        - P_{ABC}(123)P_{C}(0) - P_{ABC}(133)P_{C}(0) - P_{ABC}(200)P_{C}(0) - P_{ABC}(200)P_{C}(1) \\
        - P_{ABC}(200)P_{C}(2) - P_{ABC}(200)P_{C}(3) - P_{ABC}(201)P_{C}(0) - P_{ABC}(201)P_{C}(1) \\
        - P_{ABC}(201)P_{C}(2) - P_{ABC}(201)P_{C}(3) - P_{ABC}(203)P_{C}(1) - P_{ABC}(203)P_{C}(2) \\
        - P_{ABC}(203)P_{C}(3) - P_{ABC}(213)P_{C}(0) - P_{ABC}(223)P_{C}(0) - P_{ABC}(300)P_{C}(0) \\
        - P_{ABC}(300)P_{C}(1) - P_{ABC}(300)P_{C}(2) - P_{ABC}(300)P_{C}(3) - P_{ABC}(301)P_{C}(0) \\
        - P_{ABC}(301)P_{C}(1) - P_{ABC}(301)P_{C}(2) - P_{ABC}(301)P_{C}(3) - P_{ABC}(302)P_{C}(1) \\
        - P_{ABC}(303)P_{C}(1) - P_{ABC}(303)P_{C}(2) - P_{ABC}(303)P_{C}(3) - P_{ABC}(313)P_{C}(0) \leq 0
    \end{gathered}
    \end{equation*}
